Essays in Computational Management Science

### 2018-08-22 autocorrelationPaper/IEEEtran/to-include.tex
dangerous commit

>>>>

Let $x$ and $y$ be random bitstrings and $n$ be the number of dimensions in the memory; let $x_i$ and $y_i$ be the $i$-th bit of $x$ and $y$, respectively; and $d(x, y)$ be the Hamming distance. Whilst the probability of a shared bit-value between same dimension-bits in two random addresses is $1/2$, an address only activates hard-locations close to it.  Let us call these shared bitvalues a \emph{bitmatch in dimension $i$}.

So, what is the probability of bitmatches given that we know the access radius $r$ between the address and a hard-location?
\bigskip

\begin{theorem}
\emph{Each dimension $i$ has a small pull bias, which can be measured by}
\label{T1}
$P(x_i = y_i | d(x, y) \le r) = \dfrac{\sum_{k=0}^{r} \binom{n-1}{k}}{\sum_{k=0}^{r} \binom{n}{k}}.$
\end{theorem}

\begin{proof}
    The left-hand expression $P(x_i = y_i | d(x, y) \le r)$ computes the probability of a bitmatch in $i$, given that we know that $x$ and $y$ are in the access radius defined by $r$, i.e., $d(x, y)\le r$.

    Applying the law of total probability to the left-hand expression we obtain

    \begin{align}
    \sum_{k=0}^{r} P(x_i = y_i | d(x, y) = k \le r) P(d(x, y) = k | d(x, y) \le r)
    \end{align}

    We also know that

    \begin{align}
    P(x_i = y_i | d(x, y) = k) &= \frac{n-k}{n} \\
    P(d(x, y) = k | d(x, y) \le r) &= \frac{\binom{n}{k}}{\sum_{j=0}^{r} \binom{n}{j}}
    \end{align}

    \begin{align}
    P(x_i = y_i | d(x, y) \le r) = \frac{\sum_{k=0}^{r} \frac{n-k}{n} \binom{n}{k}}{\sum_{j=0}^{r} \binom{n}{j}}
    \end{align}

    Finally, the combinatorial identity

    \begin{align}
    \frac{n-k}{n} \binom{n}{k} = \frac{(n-k)}{n} \frac{n!}{(n-k)! k!} = \frac{(n-1)!}{k! (n-1-k)!} = \binom{n-1}{k}
    \end{align}

    closes the theorem.
